AA Distributed Software Development Methodology

### 2013-02-18 paper.tex
microlog term

In this paper we propose the AA methodology and an associated software system
for coordinating distributed team work, tackling the disadvantages
of GSD. Team members take on an egalitarian role, and stay
voluntarily \textit{logged} in the system for part of their time
(e.g.\ 2 hours per day), during which they log a periodical short text
sentence --- similar to a ``tweet'' from Twitter --- as the
status of their activity. Logging is carried out using an easy a series of
available UI's: unix shell
commands, native GUI or web page, conventional social network posts, or chat messages to a log bot
listening to IRC, GTalk, G+, and others.  These ``microblog sentences'' are publicly aggregated and validated by other
team members. Through AA, we have a methodology and an associated system to help
implement and validate the activities of a distributed software team. It implicitly
legitimizes financial support for the expansion of the activity of the developer
team. The AA methodology is specially useful for coordinating distributed and
decentralized team work, providing effective means to asynchronously update
different team members without the need for synchronous unproductive meetings.

@@

As noted, some strategies for GSD is based on complex methodologies
and many of those were built for a specific company or software
center. Here we propose an alternative methodology based on a simple
idea: small working sessions logged by a computational
tool. Figure~\ref{fig:mm} summarizes our methodology.

\begin{figure}
\begin{center}
   \includegraphics[width=0.8\linewidth,keepaspectratio=true]{figs/aa-mm.png}
\end{center}
   \caption{
   Mindmap of our methodology
   }
\label{fig:mm}
\end{figure}

@@

From the developer perspective, the AA methodology is based on
creating pretty small high perspective reports of what they are doing
in a specific time frame, that can be something between 5 to 15
minutes, depending in what is more comfortable for the developer. An
AA Session would be a period of at least 2 hours doing these
reports. The developer can set reminders to show up when its time to
make a new report. The objective of the flexible time frame and
reminders is to minimize developer overhead during his AA session. In
this way he can make the reports while staying concentrated in his
code. Each report can be sent directly to an on-line server, or stored
locally in a temporarily database for sending later. This make
possible the use of AA while offline.

>>>>

In this paper we propose the AA methodology and an associated software system
for coordinating distributed team work, tackling the disadvantages
of GSD. Team members take on an egalitarian role, and stay
voluntarily \textit{logged} in the system for part of their time
(e.g.\ 2 hours per day), during which they log a periodical short text
sentence or microlog --- similar to a ``tweet'' from Twitter --- as the
status of their activity. Logging is carried out using an easy a series of
available UI's: unix shell
commands, native GUI or web page, conventional social network posts, or chat messages to a log bot
listening to IRC, GTalk, G+, and others.  These ``microblog sentences'' are publicly aggregated and validated by other
team members. Through AA, we have a methodology and an associated system to help
implement and validate the activities of a distributed software team. It implicitly
legitimizes financial support for the expansion of the activity of the developer
team. The AA methodology is specially useful for coordinating distributed and
decentralized team work, providing effective means to asynchronously update
different team members without the need for synchronous unproductive meetings.

@@

Some of the strategies for GSD mentioned on the previous section are based on complex methodologies
and many were built for a specific company or software
center. We propose an alternative methodology based on a simple
idea: small working sessions logged by a computational
tool. Figure~\ref{fig:mm} summarizes our methodology.

\begin{figure}
\begin{center}
   \includegraphics[width=0.8\linewidth,keepaspectratio=true]{figs/aa-mm.png}
\end{center}
   \caption{
   A mindmap of our methodology
   }
\label{fig:mm}
\end{figure}

@@

From the developer's perspective, the AA methodology is based on
creating pretty small high perspective reports of what they are doing
in a specific time frame, that can be something between 5 to 15
minutes, depending on what is most convenient for the developer and the team. An
AA Session would be a period of at least 2 hours doing these periodical
micrologs. The developer can set reminders to show up when its time to
make a new report. The objective of the flexible time frame and
reminders is to minimize developer overhead during his AA session. In
this way he can make the reports while staying concentrated in his
code. Each report can be sent directly to an on-line server, or stored
locally in a temporarily database for sending later. This make
possible the use of AA while offline.
